---
title: 'Importing Stocks'
author: "Paul McCabe"
date: "November 22, 2019"
output:
  pdf_document:
    latex_engine: xelatex
    toc: true
    number_sections: true
    toc_depth: 6
    highlight: tango
  html_document:
    font-size: 10em
    self_contained: yes
    toc: yes
urlcolor: blue
---

<!--
# Script Name: Importing-Stocks.Rmd
# Purpose: This is a blank Rmd file to start importing stock data 
# Authors: Paul McCabe
# License: Creative Commons Attribution-ShareAlike 4.0 International License.
##########
# Latest Changelog Entires:
# v0.00.01 - Importing-Stocks.RMD - Paul McCabe started this blank Rmd
# v0.00.02 - Transitioning this document to specific dates for stocks, not just all stocks
##########

# Rmd code goes below the comment marker!
-->


\setcounter{section}{1}
\setcounter{subsection}{1}
\setcounter{subsubsection}{0}
# Import Stock Data
## Input start date and import list of stock names
```{r message=FALSE, warning=FALSE}
library(quantmod)
library(TTR)
library(ggplot2)
library(dplyr)
library(tidyquant)
library(plyr)
library(readr)
```
## First Steps
This version of Import-Stocks.Rmd will focus on specific stocks for specific dates. As a result, this Rmd file should be passed a dataframe with stock tickers and dates that you would like data for. We can use the same cleaning and scraping methods, but will store them differently depending on preference.

Select your file and also set a name for your task, this will be used as the folder name where the data is stored. 

```{r}

#Set these to get desired day away from transaction date
#=============
data_collection_name = "One Month"
future_date_var = 28
#=============

file_name = "date_ticker_df.csv"
comp_list_total <- read.csv(file_name)
#setwd(dirname(rstudioapi::getActiveDocumentContext()$path))

  #split up the company list into 5 parts, hopefully R Studio can handle the smaller batches
split_list <- split(comp_list_total, c("a", "b", "c", "d", "e"))
dir.create(data_collection_name)
error_list <- c()
error_list <- c(error_list, "Blank")

```
##Test 1 stock with 1 date
```{r}
date_from <- as.Date("04-11-2020", "%m-%d-%Y")
date_to <- date_from + 1
date_from
date_to
#getSymbols("ILMN", from = date_from, auto.assign= FALSE)
```
```{r} 
#initialize empty dataframe with values we wish to extract
df_test <- data.frame(date=character(), 
                      ticker=character(), 
                      Open=numeric(), 
                      High=numeric(), 
                      Low=numeric(), 
                      Close=numeric(), 
                      Volume=numeric(), 
                      Adjusted=numeric(),
                      Error_message=character(),
                      stringsAsFactors = FALSE)
#extract dates, change to date object, and add a day for the from-to range
date_test <- as.character(comp_list_total$transaction_date[1])
date_test <- as.Date(date_test, "%m-%d-%Y")
date_test
date_test2 <- as.Date(date_test, "%m-%d-%Y") + future_date_var 
date_test2 
print(weekdays(date_test2))
if (weekdays(date_test2) == "Sunday"){
  #date_test2 <- date_test2 + 1
}
if (weekdays(date_test2) == "Saturday"){
  #date_test2 <- date_test2 + 2
}
if (weekdays(date_test2) == "Friday"){
  #date_test2 <- date_test2 + 3
}
date_test3 <- date_test2 + 1

#retrieve ticker symbol and get single row of price data
ticker_test <- as.character(comp_list_total$ticker[1])
try_cond <- try(row_test <- getSymbols(ticker_test, from = date_test2, to = date_test3, auto.assign = FALSE), TRUE)
class(try_cond)
#add price data to date and ticker name, then add to empty dataframe
n = c(date_test, ticker_test)
row_total = c(n, row_test)
row_total = c(row_total, try_cond)
df_test[nrow(df_test) + 1,] <- row_total
df_test

#combining vectors has coerced them to characters, fix at the end with entire columns
```
## Create csv files from list of stock symbols
### IMPORTANT: replace the column name of split_list in the for loop condition. This will help avoid long downloads failing and having to start all over. Iterate for column a, b, c, d, e with split_list$a, split_list$b and so on... For smaller datasets, this will not be a necessary step.
```{r message=FALSE, warning=FALSE}
download_stocks <- function(comp_list, df_name){
##Checking functions for cleaning the data
  #Function that returns TRUE if the df has na values and FALSE if it has no NA values
  has_na <- function(stock_df){
    if(any(is.na(stock_df))){
      return(TRUE)
    } else {
      return(FALSE)
    }
  }
  #Function that returns TRUE if columns match the company name (correct data) and FALSE if they do not match
  column_matches <- function(company, stock_df){
    #If column name matches, then check if it has any NAs
    paste(company, ".Close") %>% 
      gsub(" ", "", .) -> c_name
    if(c_name %in% colnames(stock_df)){
      return(TRUE)
    }
    else {
      return(FALSE)
    }
  }
  #Function that returns True if there is more than 0 rows, False if there is no row
  has_rows <- function(stock_df){
    if(nrow(stock_df) < 1){
      return(FALSE)
    } else {
      return(TRUE)
    }
  }
  #Function that returns TRUE if there is a column with several zeroes, currently not being used
  has_zeroes <- function(stock_df){
    for(i in 1:ncol(stock_df)){
      print(sum(stock_df[ ,i] == 0))
      if (sum(stock_df[ ,i] == 0) >= 5){
        return(TRUE)
      }
    }  
    return(FALSE)
  }
  #Function that returns TRUE if all conditions are met
  correct_data <- function(company, stock_df){
    if((column_matches(company, stock_df) == TRUE) & (has_na(stock_df) == FALSE) & (has_rows(stock_df) == TRUE)){
      return(TRUE)
    } else {
      return(FALSE)
    }
  }
  
  
##This is where the function to download stock data starts
  stock_price_df <- data.frame(date=character(), 
                      ticker=character(), 
                      id=character(),
                      Open=numeric(), 
                      High=numeric(), 
                      Low=numeric(), 
                      Close=numeric(), 
                      Volume=numeric(), 
                      Adjusted=numeric(),
                      Error_message=character(),
                      stringsAsFactors = FALSE)
  #Change # of cycles: cycles determines how many retries downloading a stock gets
  cycles <- 2
  stock_tickers <- comp_list$ticker
  ids <- comp_list$id
  dates <- comp_list$transaction_date
  total_length <- nrow(comp_list)
  ##===========
  #new_date <- comp_list$date_1_week
  ##===========
  for (j in 1:nrow(comp_list)){
    #Display percentage to completion
    print(paste(j / total_length, "%", sep = ""))

    #extract dates and id, change to date object
    date_char <- as.character(dates[j])
    id <- as.character(ids[j])
    date_obj <- as.Date(date_char, "%m-%d-%Y") + future_date_var
    
    #retrieve ticker symbol and get single row of price data
    ticker <- as.character(stock_tickers[j])
    try_cond <- try(row_prices <- getSymbols(ticker, from = date_obj, to = date_obj + 1, auto.assign = FALSE), TRUE)
    
    #replace zeroes with NA so they turn up as errors
    try_cond2 <- try(row_prices[row_prices == 0] <- NA)
    
    #If there is an error downloading or an error in the csv file, try redownloading it until it's fine or until you pass the number of cycles
    if ((class(try_cond) == "try-error") | correct_data(ticker, row_prices) == FALSE){
      count <- 0
      while(((class(try_cond) == "try-error") | 
             correct_data(ticker, row_prices) == FALSE) & 
            count <= cycles){
        try_cond <- try(row_prices <- getSymbols(ticker, from = date_obj, to = date_obj + 1, auto.assign = FALSE), TRUE)
        count <- count + 1
      }
    }
    
    #If there is still an error, store the error message in the dataframe column, Error_message
    if(class(try_cond) == "try-error"){
      row_total = c(date_char, ticker, id, row_prices, try_cond)
      } else {
      row_total = c(date_char, ticker, id, row_prices, "None")
      }
    
    #add price data to date and ticker name, then add to empty dataframe
    stock_price_df[nrow(stock_price_df) + 1,] <- row_total
  }
  save_location = paste(data_collection_name, df_name, sep="")
  write_csv(stock_price_df, save_location)
}
#download from list of stocks
#change df_name and stock_df to splitlist$a if you wish to split the downloading
df_name = "/stock_price_dfe.csv"
stock_df = split_list$e
download_stocks(stock_df, df_name)
```
## Company Error List Function
```{r}
#create an error list based on what files were downloaded and the original list of stocks that were supposed to be downloaded
create_error_list <- function(){
  remove_prefix <- function(name){
    return(gsub("^.*?/","", name) %>% gsub(".csv", "", .) %>% gsub(" ", "", .))
  }
  list_names <- list.files(path = start_date, pattern = "*.csv", full.names = T)
  x <- c()
  for (name in list_names){
    x <- c(x, remove_prefix(name))
  }
  error_list <- comp_list_total[!(comp_list_total %in% x)]
  
  write.csv(error_list, "company_error_list.csv")
}
create_error_list()
```

## Getting Rid of Errors (Loop through error list and apply the same function)
```{r}
error_list <- read.csv("company_error_list.csv")$x
download_stocks(error_list)
create_error_list()
```

## Test 1 stock
```{r message=FALSE, warning=FALSE}
directory <- paste(start_date, "/", company, ".csv", sep = "")

name <- names_adjusted_2[2]
test_stock <- read.csv(name)

gsub("^.*?/","", name) %>% gsub(".csv", "", .) %>% paste(., ".Close") %>% gsub(" ", "", .) -> close_name
#ggplot(data = test_stock, aes_string(x = "X", y = close_name)) + geom_point()

paste(comp_name, ".Open") %>% gsub(" ", "", .) -> open_name
paste(comp_name, ".High") %>% gsub(" ", "", .) -> high_name
paste(comp_name, ".Low") %>% gsub(" ", "", .) -> low_name
paste(comp_name, ".Volume") %>% gsub(" ", "", .) -> volume_name

test_stock %>%
    ggplot(aes(x = X, y = close_name)) + geom_candlestick(aes_string(open = open_name, high = high_name, low = low_name, close = close_name)) + geom_ma(color = "darkgreen")

ggplot(test_stock, aes_string(x="X", y = volume_name))+geom_bar(stat="identity")
#+geom_bar(aes_string(x = "X", y = volume_name), stat = "identity")
#MACD <- as.data.frame(MACD(test_stock$AAL.Adjusted, nFast=12, nSlow=26,nSig=9,maType=SMA, percent = TRUE))
#MACD <- cbind(index = rownames(MACD), MACD)
#rownames(MACD) <- 1:nrow(MACD)

#ggplot() + 
  #geom_point(data = MACD, aes(x = index, y = macd, color = "Blue"))+geom_line(data = test_stock, aes(x = X, y = AAL.Adjusted))
```

```{r}
test_stock <- as.data.frame(getSymbols("WYNN", from = start_date, auto.assign = FALSE))
test_stock["Date"] <- as.Date(row.names(test_stock))
test_stock %>%
  mutate(Variability = (WYNN.High - WYNN.Low) / WYNN.Open) %>% 
  mutate(Percent.Change = abs(WYNN.Open - WYNN.Close) / WYNN.Open) %>% 
  mutate(Var.minus.perc = Variability - Percent.Change) %>%
  ggplot(.)+geom_line(aes(x=Date, y=Variability))+ geom_line(aes(x=Date, y=Percent.Change), color = "blue") + geom_line(aes(x=Date, y=Var.minus.perc), color = "green")
```
#### Links
 
http://www.r-project.org 

http://rmarkdown.rstudio.com/  

<!--
# Complete Change Log History
# v0.00.00 - 1405-07 - Paul McCabe made the blank script
# v0.00.01 - Paul removed stocks with names that don't match data
# v0.00.02 - Paul removed stocks with NA values
##########

-->